---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# ggpirate

A [pirate plot](https://cran.r-project.org/web/packages/yarrr/vignettes/pirateplot.html) is a way of displaying data where a continuous dependent variable is a function of a categorical independent variable, in a more informative way than the traditional barplot. `geom_pirate()` plots the raw data as points (using `ggplot2::geom_jitter()`), along with layers showing descriptive and inferential statistics -- bars indicating means (using `ggplot2::geom_col()`), horizontal line indicating means (using `ggplot2::geom_crossbar()`), boxes indicating 95\% confidence intervals assuming a normal sampling distribution (using `ggplot2::geom_rect()`), and violins indicating the density (using `ggplot2::geom_violin()`).


## Installation

You can install ggpirate from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("mikabr/ggpirate")
```


# Examples

```{r setup, message = FALSE}
library(ggpirate)
theme_set(theme_bw())
```

Colour pirate plot:
```{r colour}
ggplot(mpg, aes(x = class, y = displ)) +
  geom_pirate(aes(colour = class, fill = class))
```

Black and white pirate plot:
```{r bw}
ggplot(mpg, aes(x = class, y = displ)) +
  geom_pirate()
```
