---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r knitr, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# ggpirate

A [pirate plot](https://cran.r-project.org/web/packages/yarrr/vignettes/pirateplot.html) is a way of displaying data where a continuous dependent variable is a function of a categorical independent variable, in a more informative way than the traditional barplot. `geom_pirate()` plots the raw data as points (using `ggplot2::geom_jitter()`), along with layers showing descriptive and inferential statistics -- bars indicating means (using `ggplot2::geom_col()`), horizontal line indicating means (using `ggplot2::geom_crossbar()`), boxes indicating 95\% confidence intervals assuming a normal sampling distribution (using `ggplot2::geom_tile()`), and violins indicating the density (using `ggplot2::geom_violin()`).


## Installation

You can install ggpirate from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("mikabr/ggpirate")
```


# Examples

```{r setup, message = FALSE}
library(ggpirate)
theme_set(theme_bw())
```

Colour pirate plot:
```{r colour}
ggplot(mpg, aes(x = class, y = cty)) +
  geom_pirate(aes(colour = class, fill = class))
```

Each of the layers can be turned off, e.g. for just means and confidence intervals:
```{r layers}
ggplot(mpg, aes(x = class, y = cty)) +
  geom_pirate(aes(colour = class),
              points = FALSE, bars = FALSE, violins = FALSE)
```

Colour can be mapped to a different variable than the x axis, resulting in dodged subgroups:
```{r dodge}
mpg2 <- dplyr::mutate(mpg, drv = factor(drv))

ggplot(mpg2, aes(x = class, y = cty)) +
  geom_pirate(aes(colour = drv, fill = drv), show.legend = TRUE)
```

And it plays well with facetting:
```{r facets, fig.width=8}
mpg_gather <- tidyr::gather(mpg, type, mileage, cty, hwy)

ggplot(mpg_gather, aes(x = class, y = mileage)) +
  facet_wrap(~type) +
  geom_pirate(aes(colour = class, fill = class))
```

Finally, the parameters passed to any of the layers can be adjusted, e.g.:
```{r params}
ggplot(mpg, aes(x = class, y = cty)) +
  geom_pirate(aes(colour = class), bars = FALSE,
              points_params = list(shape = 19, alpha = 0.2),
              lines_params = list(size = 0.8))
```
